\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
abstract: change in sentence

\abstract{The disconnected part of the power spectrum covariance matrix (also known as the ``Gaussian'' covariance) is the dominant contribution on large scales for galaxy clustering and weak lensing datasets. The presence of a complicated sky mask causes non-trivial correlations between different Fourier/harmonic modes, which must be accurately characterised in order to obtain reliable cosmological constraints. This is particularly relevant for galaxy survey data. Unfortunately, an exact calculation of these correlations involve $O(\ell_{\rm max}^6)$ operations that become computationally impractical very quickly. We present an implementation of approximate methods to estimate the Gaussian covariance matrix of power spectra involving spin-0 and spin-2 flat- and curved-sky fields, expanding on existing algorithms. These methods achieve an $O(\ell_{\rm max}^3)$ scaling, which makes the computation of the covariance matrix as fast as the computation of the power spectrum itself. We quantify the accuracy of these methods on large-scale structure and weak lensing data, making use of a large number of Gaussian but otherwise realistic simulations. We show that, using the covariance matrix computing using these approximations we are able to recover the true posterior distribution cosmological parameters to high accuracy. We also quantify the shortcomings of these methods, which become unreliable on the very largest scales, as well as for covariance matrix elements involving lensing $B$ modes. The algorithms presented here are implemented in the public code {\tt NaMaster} \url{https://github.com/LSSTDESC/NaMaster}.}

>>>>

\abstract{The disconnected part of the power spectrum covariance matrix (also
  known as the ``Gaussian'' covariance) is the dominant contribution on large
  scales for galaxy clustering and weak lensing datasets. The presence of a
  complicated sky mask causes non-trivial correlations between different
  Fourier/harmonic modes, which must be accurately characterised in order to
  obtain reliable cosmological constraints. This is particularly relevant for
  galaxy survey data. Unfortunately, an exact calculation of these
  correlations involve $O(\ell_{\rm max}^6)$ operations that become
  computationally impractical very quickly. We present an implementation of
  approximate methods to estimate the Gaussian covariance matrix of power
  spectra involving spin-0 and spin-2 flat- and curved-sky fields, expanding
  on existing algorithms. These methods achieve an $O(\ell_{\rm max}^3)$
  scaling, which makes the computation of the covariance matrix as fast as the
  computation of the power spectrum itself. We quantify the accuracy of these
  methods on large-scale structure and weak lensing data, making use of a
  large number of Gaussian but otherwise realistic simulations. We show that,
  using the approximated covariance matrix, we are able to recover
  the true posterior distribution of cosmological parameters to high accuracy. We also quantify the shortcomings of these methods, which become unreliable on the very largest scales, as well as for covariance matrix elements involving lensing $B$ modes. The algorithms presented here are implemented in the public code {\tt NaMaster} \url{https://github.com/LSSTDESC/NaMaster}.}
